Data Processing: Population Estimates

### 2021-11-28 code/processing_code/processing-populations.Rmd
Outlier Analysis

* FIPStxt
* State
* Area.name
* Population.2020
```{r variable selection}
#select key variables
pops_1 <- populations_raw %>%
                dplyr::select(FIPStxt,
                              State,
                              Area.name,
                              Population.2020)
```
We will eventually get rid of FIPStxt, but we need it to separate state and county level data.

>>>>

* FIPStxt
* State
* Area.name
* Population.2020
```{r variable selection}
#select key variables
pops_1 <- populations_raw %>%
                dplyr::select(ï..FIPStxt,
                              State,
                              Area.name,
                              Population.2020) %>%
               dplyr::rename(FIPStxt = ï..FIPStxt)
```
We will eventually get rid of FIPStxt, but we need it to separate state and county level data.
